SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-26 scipy-1.0/paper.tex
First round of revisions based on reviewer feedback in manuscript PR 43.

>>>>

\texttt{scipy.sparse} offers seven sparse matrix data structures. 
The most important ones are CSR and CSC; these offer fast row or column 
access and fast matrix-vector multiplication, and are used heavily in 
scikit-learn.

Over the last three years our sparse matrix handling internals have
been rewritten and performance has been improved. Iterating over 
and slicing of CSC and CSR matrices is now faster by up to 35\%,
and the CSR to COO matrix format conversion is now several times faster.
COO matrices are now generally more memory efficient. Importantly,
SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing
the low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively.
